---
title: "MI - AGI: Simulated data"
author: "Emily Nazario"
date: "`r Sys.Date()`"
format:
 html: 
  embed-resources: true
editor: visual
toc: TRUE
toc-title: "On this page"
theme: yeti
fontcolor: "#134f5c"
---

```{r}
#| include: false
#| echo: false
#| warning: false
#| label: libraries

library(tidyverse)
library(tidyquant)
library(terra)
library(sf)
library(here)
library(rnaturalearth)
library(rnaturalearthdata)
library(wesanderson)
source(here("functions/oxy_demand_functions.R"))
set.seed(0904)

shore <- ne_download(scale = "medium", type = "land", category = "physical", returnclass = "sf")
mid_atlantic_bbox <- st_bbox(c(xmin = -77, xmax = -68, ymin = 34, ymax = 42), crs = st_crs(shore))
mid_atlantic_coast <- st_crop(shore, mid_atlantic_bbox)

```

## Simulate enviro data

```{r}
#| warning: false
#| label: simu

enviro_sim <- data.frame(lat = runif(100, min = 34, max = 42), 
                         long = runif(100, min = -77, max = -68), 
                         DO_atm = runif(100, min = 0.10, max = 0.20), 
                         temp = runif(100, min = 0, max = 30))

DO_thresh <- quantile(enviro_sim$DO_atm)[1]

```

## Calculate MI and AGI

::: panel-tabset

### Black sea bass

```{r}
#| warning: false
#| label: calc bass

### MI ####
enviro_bass <- enviro_sim %>% mutate(DO_kpa = DO_atm*101.325)
enviro_bass$mi <- MI_calc(A0 = 0.00040728, Bn = 0.01, DO_kPa = enviro_bass$DO_kpa, E0 = 0.27, kB = 0.00008617333262, T_C = enviro_bass$temp)
hist(enviro_bass$mi)

### AGI ####
enviro_bass$agi_o2_demand <- OxyDemand(Tpref = 22, PO2_thresh = DO_thresh, T_C = enviro_bass$temp, W = 498.95, d = 0.700, K = 0.231, j2 = 8, j1 = 4.5, 
                                      Linf = 34.1, LwA = 0.02661, LwB = 2.8)
enviro_bass$agi <- enviro_bass$DO_atm/enviro_bass$agi_o2_demand
hist(enviro_bass$agi)

```

### Atlantic cod

Used same simulated data for both species. Though normative temperatures would be much lower for cod than bass. Weight is average reported online. 

```{r}
#| warning: false
#| label: calc cod

### MI ####
enviro_cod <- enviro_sim %>% mutate(DO_kpa = DO_atm*101.325)
enviro_cod$mi <- MI_calc(A0 = 0.000000668, Bn = 0.01, DO_kPa = enviro_cod$DO_kpa, E0 = 0.42, kB = 0.00008617333262, T_C = enviro_cod$temp)
hist(enviro_cod$mi)

### AGI ####
enviro_cod$agi_o2_demand <- OxyDemand(Tpref = 12, PO2_thresh = DO_thresh, T_C = enviro_cod$temp, W = 39916.1, d = 0.700, K = 0.121, j2 = 8, j1 = 4.5, 
                                      Linf = 148, LwA = 0.005, LwB = 3.185)
enviro_cod$agi <- enviro_cod$DO_atm/enviro_cod$agi_o2_demand
hist(enviro_cod$agi)

```

:::

## Size explore (AGI oxygen demand, units: atm)

**Linf (according to von Bertalanffy growth theory)** = NOT the maximum length of the animal. Instead, it is the length a species would reach if it continued to grow indefinitely. Horizontal asymptote of the asymptotic growth curve.  

**Winf (according to Fishbase)** = A parameter of the von Bertalanffy Growth Function (VBGF), expressing the mean weight the fish of a given stock would reach if they were to grow for an infinitely long period; also: the weight corresponding to Linf. 

::: panel-tabset

### Black sea bass weight

Min and max weights from the MI study
```{r}
#| warning: false
#| label: W bass

#max weight for species
enviro_bass$agi_o2_demand <- OxyDemand(Tpref = 22, PO2_thresh = DO_thresh, T_C = enviro_bass$temp, W = 700.4, d = 0.700, K = 0.231, j2 = 8, j1 = 4.5, 
                                      Linf = 34.1, LwA = 0.02661, LwB = 2.8)
hist(enviro_bass$agi_o2_demand)

#min weight for species
enviro_bass$agi_o2_demand <- OxyDemand(Tpref = 22, PO2_thresh = DO_thresh, T_C = enviro_bass$temp, W = 193.7, d = 0.700, K = 0.231, j2 = 8, j1 = 4.5, 
                                      Linf = 34.1, LwA = 0.02661, LwB = 2.8)
hist(enviro_bass$agi_o2_demand)

```

### Atlantic cod weight

Min and max weights used here are just for **juveniles** included in MI study. 
```{r}
#| warning: false
#| label: W cod

#max weight for species
enviro_cod$agi_o2_demand <- OxyDemand(Tpref = 12, PO2_thresh = DO_thresh, T_C = enviro_cod$temp, W = 473, d = 0.700, K = 0.121, j2 = 8, j1 = 4.5, 
                                      Linf = 148, LwA = 0.005, LwB = 3.185)
hist(enviro_cod$agi_o2_demand)

#min weight for species
enviro_cod$agi_o2_demand <- OxyDemand(Tpref = 12, PO2_thresh = DO_thresh, T_C = enviro_cod$temp, W = 79, d = 0.700, K = 0.121, j2 = 8, j1 = 4.5, 
                                      Linf = 148, LwA = 0.005, LwB = 3.185)
hist(enviro_cod$agi_o2_demand)

```

### Black sea bass length (Winf via Linf)

Min and max TL from MI study. Weights are average from MI study (Slessinger et al., 2019; 329.9 g)
```{r}
#| warning: false
#| label: Winf bass

#max length for species -- max weight included in MI study
enviro_bass$agi_o2_demand <- OxyDemand(Tpref = 22, PO2_thresh = DO_thresh, T_C = enviro_bass$temp, W = 329.9, d = 0.700, K = 0.231, j2 = 8, j1 = 4.5, 
                                      Linf = 39.8, LwA = 0.02661, LwB = 2.8)
hist(enviro_bass$agi_o2_demand)

#min length for species -- min weight included in MI study
enviro_bass$agi_o2_demand <- OxyDemand(Tpref = 22, PO2_thresh = DO_thresh, T_C = enviro_bass$temp, W = 329.9, d = 0.700, K = 0.231, j2 = 8, j1 = 4.5, 
                                      Linf = 22.1, LwA = 0.02661, LwB = 2.8)
hist(enviro_bass$agi_o2_demand)

```

### Atlantic cod length (Winf via Linf)

Min and max TLs used here are just for juveniles included in MI study. Weights are average from MI study from SMR results at 10C.
```{r}
#| warning: false
#| label: Winf cod

#max length for species -- max weight included in MI study
enviro_cod$agi_o2_demand <- OxyDemand(Tpref = 12, PO2_thresh = DO_thresh, T_C = enviro_cod$temp, W = 157.7, d = 0.700, K = 0.121, j2 = 8, j1 = 4.5, 
                                      Linf = 39, LwA = 0.005, LwB = 3.185)
hist(enviro_cod$agi_o2_demand)

#min length for species -- max weight included in MI study
enviro_cod$agi_o2_demand <- OxyDemand(Tpref = 12, PO2_thresh = DO_thresh, T_C = enviro_cod$temp, W = 157.7, d = 0.700, K = 0.121, j2 = 8, j1 = 4.5, 
                                      Linf = 21, LwA = 0.005, LwB = 3.185)
hist(enviro_cod$agi_o2_demand)

```

:::

## Calculated metabolic demand (AGI denominator) vs. empirical

::: panel-tabset

### Black sea bass

Empirical data taken from target temperature binned averages from Slessinger et al., 2019. Sexes were mixed to calculate temperature specific averages. RMR are reported as mg O2/hr/kg. AGI-MR values are in atm. 
```{r}
#| warning: false
#| label: met bass

emp_bass_test <- data.frame(temp = as.numeric(c(12, 17, 22, 24, 27)), 
                           RMR = as.numeric(c(47.68, 69.28, 94.42, 117.93, 142.5))) 

emp_bass_test$agi_o2_demand <- OxyDemand(Tpref = 22, PO2_thresh = DO_thresh, T_C = emp_bass_test$temp, W = 498.95, d = 0.700, K = 0.231, j2 = 8, j1 = 4.5, 
                                      Linf = 34.1, LwA = 0.02661, LwB = 2.8)

ggplot(emp_bass_test, aes(x = RMR, y = agi_o2_demand, fill = temp)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray40") +  # 1:1 line
  geom_point(shape = 21, size = 4, color = "black") +  
  scale_fill_gradientn(colors = wes_palette("Zissou1", 100, type = "continuous")) +
  theme_minimal() +
  labs(
    x = "RMR",
    y = "AGI oxygen demand",
    fill = "Temperature (°C)"
  )

```


### Atlantic cod 

Empirical data taken from target temperature binned averages from Schurmann and Steffensen 1997. Values were pulled from table 1 of the paper. RMR are reported as mg O2/hr/kg. AGI-MR values are in atm.
```{r}
#| warning: false
#| label: met cod

emp_cod_test <- data.frame(temp = as.numeric(c(5, 10, 15)), 
                           SMR = as.numeric(c(35.5, 57, 78.2))) 

emp_cod_test$agi_o2_demand <- OxyDemand(Tpref = 12, PO2_thresh = DO_thresh, T_C = emp_cod_test$temp, W = 39916.1, d = 0.700, K = 0.121, j2 = 8, j1 = 4.5, Linf = 148, LwA = 0.005, LwB = 3.185)

ggplot(emp_cod_test, aes(x = SMR, y = agi_o2_demand, fill = temp)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray40") +  # 1:1 line
  geom_point(shape = 21, size = 4, color = "black") +  
  scale_fill_gradientn(colors = wes_palette("Zissou1", 100, type = "continuous")) +
  theme_minimal() +
  labs(
    x = "SMR",
    y = "AGI oxygen demand",
    fill = "Temperature (°C)"
  )

```

:::


<!--
Scratch docs from old explore


```{r}
#| warning: false
#| label: mi_figs

## Plot
### MI

## Just done for black sea bass explore

#DO vs. MI
# ggplot(enviro_sim, aes(DO_kpa, mi))+
#   geom_point(size = 2)+
#   theme_tq()
# 
# #temp vs. MI
# ggplot(enviro_sim, aes(temp, mi))+
#   geom_point(size = 2)+
#   theme_tq()
# 
# #temp, DO, MI
# ggplot(enviro_sim, aes(temp, DO_kpa))+
#   geom_point(size = 4, aes(color = mi))+
#   theme_tq()
# 
# #map
# ggplot() +
#   geom_point(data = enviro_sim, aes(x = long, y = lat, color = mi), size = 3) +
#   scale_color_viridis_c(option = "plasma", name = "AGI") +
#   geom_sf(data = mid_atlantic_coast, fill = "grey70") +
#   coord_sf(xlim = c(-77, -68), ylim = c(34.5, 42), expand = FALSE) +
#   theme_tq()


```


```{r}
#| warning: false
#| label: agi_figs

### AGI
## Just done for black sea bass explore


#DO vs. AGI
# ggplot(enviro_sim, aes(DO_atm, agi))+
#   geom_point(size = 2)+
#   theme_tq()
# 
# #temp vs. AGI
# ggplot(enviro_sim, aes(temp, agi))+
#   geom_point(size = 2)+
#   theme_tq()
# 
# #temp, DO, AGI
# ggplot(enviro_sim, aes(temp, DO_atm))+
#   geom_point(size = 4, aes(color = agi))+
#   theme_tq()
# 
# #map
# ggplot() +
#   geom_point(data = enviro_sim, aes(x = long, y = lat, color = agi), size = 3) +
#   scale_color_viridis_c(option = "plasma", name = "AGI") +
#   geom_sf(data = mid_atlantic_coast, fill = "grey70") +
#   coord_sf(xlim = c(-77, -68), ylim = c(34.5, 42), expand = FALSE) +
#   theme_tq()

```

-->